---
title: "Project Proposal Template"
authors: YOUR NAME and YOUR NAME and YOUR NAME
format: 
  pdf:
    embed-resources: true 
---

```{=html}
<style type="text/css">
h1.title {
  font-size: 40px;
  text-align: center;
}
</style>
```

```{r setup, include=FALSE}
# load all necessary packages here
```

DELETE THIS PARAGRAPH: You should replace all text in this template with the requested content. You will lose 10% of the points on this assignment if the title of your project proposal is still "Project Proposal Template," (provide your own title even if it's just "STAT 330 Project Proposal") or if the text in each section isn't replaced with your own words, **written in complete sentences and paragraphs.** You should also delete the pre-existing comments in the code blocks of this template, providing your own comments where appropriate.

# 1 Group Members

DELETE THIS: List the names of all group members in this section. (Don't forget to delete this part! The only content in this section should be a sentence like "The members of our group are...")

# 2 Data Set

DELETE THIS: What dataset do you intend to use for your final project? Where can it be found? **Provide a thorough description of the data set and the variables it contains.** Load your data into R and print the first few rows of the data set.

```{r}
#Read your data into R. 
#You will eventually need to provide a copy of the data to the
#professor as part of the final project submission, so it
#probably makes sense to download a copy of the data to your
#machine rather than call the data from a url.

#proj_data = read.table("PATH_TO_DATA")
```

# 3 Potential Questions of Interest

DELETE THIS: What are two scientific questions you could try to answer by applying regression tools to this dataset? **Provide commentary on why someone might be interested in studying these questions.**

# 4 Exploratory Data Analysis

DELETE THIS: Conduct EDA and provide **at least 3** figures or statistics highlighting features or between variable relationships within the data that are relevant to the questions of interest you provided earlier in the proposal. **You should explain what you found interesting or noteworthy about each of 3 included elements.**

```{r}
#Code for your EDA here. 
#Can you come up with useful visualizations of your data 
#that might help someone gain insight into your questions of interest 
#prior to any formal statistical analysis being conducted?
```

# 5 Preliminary Model Fit

DELETE THIS: Select a variable from your dataset that makes sense to describe as a dependent or response variable, and another to describe as an explanatory or predictor variable.

DELETE THIS: **Write out the model you have chosen** (in proper mathematical notation) and fit it using R. The SLR model you fit doesn't have to directly relate to one of your research questions, but **you should provide a brief justification of why someone may be interested in the relationship characterized by your initial model.**

```{r}
#lm.fit = lm(response~predictor, data = proj_data)
```

DELETE THIS: Do the following:

-   Assess whether the regression assumptions are satisfied

-   Provide interpretation for the estimated coefficients for $\beta_0$ and $\beta_1$. Do so in context of the uncertainty on these estimates.

-   Provide interpretation for the estimated variance parameter.

You are welcome to use as many or as few code blocks as you wish in this section, but make sure that your analysis is easy to follow.

```{r}
#Assess assumptions

#Interpret model output contained in summary(lm.fit)
```
